---
title: "What time of day should you fly if you want to avoid delays as much as possible?"
author: "Jingyun Jia"
date: "2021/10/5"
output: github_document
---
# 1.Conclusion
1. Autumm is the best season to fly in 2013.
2. I recommend to fly before 10am in each season.
3. In general cases, there is no apparent diference whether it is windy.(This is kind of weild.)

# 2.Some Preparations
I set a criterion for delay: if both dep_delay and arr_delay are greater than zero, or it is NA, it is a delay flight.
Then I add a logical variable called 'delay' (0:not delay;1:delay).
```{r}
library(nycflights13)
library(dplyr)
library(lubridate)
library(ggplot2)
library(tidyr)
library(hydroTSM)
weather1=weather%>%select(visib,wind_speed,precip,time_hour)
flights1=flights%>%left_join(weather1,by='time_hour')%>%
  mutate(delay=(dep_delay>0)*(arr_delay>0),season=time2season(time_hour,out.fmt="seasons"))
flights1$delay=flights1$delay%>%replace_na(1)
flights11=flights1%>%select(month,season,hour,visib,wind_speed,precip,delay)

```
# 3.Analysis
## 3.1.Season
I culculate the proportion of delay flights in each season and autumm has a lowest proportion and there is a huge difference among autumm and other seasons.
```{r}
# hour
flights11%>%group_by(season)%>%summarise(delay_portion=sum(delay)/n()) 
```
## 3.2.Hour(Interact with season)
I think this is the most important factor to cause delay, and it can also influent weather.
From the lineplot, the four lines show nearly the same tendency, but in summer after 10pm, there is a upward tendency.
In addition, in the period of 0-5am, it is apparently some outliers since the delay-proportion is 1.
```{r}
# season,hour
flights11%>%group_by(hour,season)%>%summarise(delay_portion=sum(delay)/n())%>%ggplot()+geom_line(aes(x=hour,y=delay_portion,color=season)) 
```
## 3.2.Weather(Wind Speed)
Actually, I want to explore more factors about weather, but there is almost no difference in other weather variables. 
For example, nearly all hours' visible is 10 and all hours' precipitation is 0. THerefore, I only choose one factor, wind speed, to find some pattern.
However, from the boxplot, there are no significant differences between to groups.
```{r}
# wind_speed
flights11%>%ggplot(aes(x=as.factor(delay),y=wind_speed))+geom_boxplot()
```
